### 2015-07-26 doc/manual/inputParameters.tex
Added magneticDriftDerivativeScheme to user manual

\param{ExBDerivativeScheme}
{integer}
{0}
{Whenever the radial electric field is nonzero}
{Options for controlling upwinding of the $\vect{E}\times\vect{B}$ drift terms.  Note the options are different than for \parlink{thetaDerivativeScheme}
and \parlink{zetaDerivativeScheme}.  This option exists because when the radial electric field is large enough to be comparable to the resonance,
such that the coefficient in front of the $\partial f/\partial \theta$ or $\partial f/\partial\zeta$ terms vanishes near the thermal speed of one of the species,
the distribution function can develop unphysical grid-scale structure.  This option allows upwinding of these spatial derivatives, which eliminates the grid-scale oscillations.\\

@@

The different settings require slightly different amounts of memory for factorization due to the different numbers of nonzeros. Option 1 requires the least memory, then 0, then 2,
and 3 requires the most.  The difference in memory required appears to be small, around 10\%.
On the other hand, the denser the stencil, the more accurate the result. Hence, in order from least to most accurate, the options are 1, 0, 2, 3.
You should use the default {\ttfamily ExBDerivativeScheme} = 0 except for very large radial electric fields, when the electric field is as large as the resonance or larger.
In this case, {\ttfamily ExBDerivativeScheme} = 3 is recommended.
}

>>>>

\param{ExBDerivativeScheme}
{integer}
{0}
{Whenever the radial electric field is nonzero}
{Options for controlling upwinding of the $\vect{E}\times\vect{B}$ drift terms.  Note the options are different than for \parlink{thetaDerivativeScheme}
and \parlink{zetaDerivativeScheme}, and are analogous to the options for \parlink{magneticDriftDerivativeScheme}.
This option exists because when the radial electric field is large enough to be comparable to the resonance,
such that the coefficient in front of the $\partial f/\partial \theta$ or $\partial f/\partial\zeta$ terms vanishes near the thermal speed of one of the species,
the distribution function can develop unphysical grid-scale structure.  This option allows upwinding of these spatial derivatives, which eliminates the grid-scale oscillations.\\

@@

The different settings require slightly different amounts of memory for factorization due to the different numbers of nonzeros. Option 1 requires the least memory, then 0, then 2,
and 3 requires the most.  The difference in memory required appears to be small, around 10-20\% between settings 1 and 3.
On the other hand, the denser the stencil, the more accurate the result. Hence, in order from least to most accurate, the options are 1, 0, 2, 3.
Option 1 is substantially less accurate than the other options.
You should use the default {\ttfamily ExBDerivativeScheme} = 0 except for very large radial electric fields, when the electric field is as large as the resonance or larger.
In this case, {\ttfamily ExBDerivativeScheme} = 3 is recommended.
}

\param{magneticDriftDerivativeScheme}
{integer}
{3}
{Whenever \parlink{magneticDriftScheme} is nonzero}
{Options for controlling upwinding of the magnetic drift terms.  Note the options are different than for \parlink{thetaDerivativeScheme}
and \parlink{zetaDerivativeScheme}, and are analogous to the options for \parlink{ExBDerivativeScheme}.
This option exists because when magnetic drift terms involving $\partial f/\partial \theta$ and $\partial f/\partial\zeta$
are implemented using the same centered difference stencil as the parallel streaming term,
the distribution function can develop unphysical grid-scale structure.  This option allows upwinding of these spatial derivatives, which eliminates the grid-scale oscillations.\\

{\ttfamily magneticDriftDerivativeScheme} = 0: Use same differentiation matrices for the magnetic drift terms as for the parallel streaming term.\\

{\ttfamily magneticDriftDerivativeScheme} = 1: Treat the magnetic drift terms using a 4 point upwinded stencil (1 point on 1 side, 2 points on the other.)\\

{\ttfamily magneticDriftDerivativeScheme} = 2: Treat the magnetic drift terms using a 5 point upwinded stencil (1 point on 1 side, 3 points on the other.)\\

{\ttfamily magneticDriftDerivativeScheme} = 3: Treat the magnetic drift terms using a 6 point upwinded stencil (2 points on 1 side, 3 points on the other.)\\

The different settings require slightly different amounts of memory for factorization due to the different numbers of nonzeros. Option 1 requires the least memory, then 0, then 2,
and 3 requires the most.  The difference in memory required appears to be small, around 10-20\% between settings 1 and 3.
On the other hand, the denser the stencil, the more accurate the result. 
Hence, in order from least to most accurate, the options are 1, 0, 2, 3. Option 1 is substantially less accurate than the other options.
The default setting of 3 is robust and recommended in most cases.
}
